---
title       : BAC Presentation
subtitle    : Windmark BAC algorithm
author      : Liam Moorfield-Yee
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Description of Program

The program takes 3 inputs and calculates the BAC for a standard male using the Windmark BAC algorithm. 

--- .class #id 

## Inputs

The variables are as follows:

- drinks -> Standard Drinks Consumed 
- weight -> Body Weight in pounds
- time -> Time Elapsed Drinking in hours

--- .class #id

## Calculations

The windmark algorithm calculates BAC by dividing total alcohol content consumed (g) by weight(g)*rm, where rm is the gender constant for males and is equal to .68. The ratio is then multiplied by 100, which returns BAC as a percentage, and adjusted for time elapsed.

The resulting algorithm is:

```{r, echo = TRUE}
bac <- function(Drinks, weight, time){ (((as.numeric(Drinks)*14)/(as.numeric(weight)* 453.592 * 0.68))*100 - (as.numeric(time)*0.015))}
```

--- .class #id

## Example

The BAC for a 100 pound man who has had 2 drinks in the past hour is:

```{r}
(((2)*14)/(100* 453.592 * 0.68))*100 - (1*0.015)
```

--- .class #id

## Significance

This is a very simple algorithm that will can be used to help people better understand how drinking affects their bodies.

--- .class #id

## Thank You For Watching!!!

--- .class #id




